A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-20 tex/body.tex
more

This work is part of a program that aims at enriching automatic provers
with high-level features and at reducing the gap between automatic and
interactive theorem proving. As future work, it would be useful to implement
proof reconstruction for (co)data\-type inferences in Isabelle.
CVC4 cound be interfaced for generating counterexamples in proof assistants, as
an alternative to Nitpick; in this context, the acyclicity and uniqueness
rules are essential to exclude spurious models. Finally, it might be
worthwhile to extend SMT solvers with dedicated support for (co)recursive
functions.

>>>>

This work is part of a program that aims at enriching automatic provers
with high-level features and at reducing the gap between automatic and
interactive theorem proving. As future work, it would be useful to implement
proof reconstruction for (co)data\-type inferences in Isabelle.
CVC4 cound be interfaced for generating counterexamples in proof assistants, as
an alternative to Nitpick; in this context, the acyclicity and uniqueness
rules are crucial to exclude spurious models. Finally, it might be
worthwhile to extend SMT solvers with dedicated support for (co)recursive
functions.
